Towards a probability measure approach for Differential Privacy in Bayesian inference

### 2018-07-24 main-fullversion.tex
rename file
fix mistakes
update full version

\input{macros}

@@

		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are:

		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
		 \hline
		\end{tabular}
		\end{center}

@@

		\item keep the prior unchanged, $\betad(1,1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for 60 times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$

		\begin{center}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
		 \hline
		 \multicolumn{3}{c}{$\cdots$}  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
		 \hline
		\end{tabular}
		\end{center}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.5\textwidth]{sensitivity}
\label{fig_sensitivity}
\caption{Hellinger distance study}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_2.eps}}
  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.48\textwidth]{accuracy_box_1.eps}} 
\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
\label{fig_beta_hellinger}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
    \includegraphics[width=0.48\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
\label{fig_dirichlet_hellinger}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
  \subfigure[accuracy measurement based on $l_1$ norm]{
    \includegraphics[width=0.48\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
\label{fig_dirichlet_hellinger_l1}
\end{center}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.48\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Accuracy measurement based on Hellinger distance wrt. different datasizes. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$}
\label{fig_vs_datasize}
\end{center}
\end{figure*}

In Fig. \ref{fig_vs_datasize}, both of the two plots show that when data size go larger, accuracy of our exponential mechanism are decreasing. In Fig. \ref{fig_vs_datasize}(a), when the data size is smaller than 12, we can beta Laplace mechanism but fail when data size larger than or equal to 12. Same as in Fig. \ref{fig_vs_datasize}(b), we can beat Laplace mechanism when data size is smaller than 15 and fail otherwise.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_dimension}
\caption{Accuracy measurement based on Hellinger distance wrt. different dimensions and data size. Settings: observed data are uniformly distributed, $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_dimension}
\end{figure}

In Fig. \ref{fig_vs_dimension}, x-axis are observed data sets of different size and dimensions. The plot shows that dimensions have similar influence on our exponential mechanism and the Laplace mechanism. Accuracy of two mechanisms both decrease when dimensions go larger. We will be beat by Laplace mechanism when data size increase but will not be affected when dimensions increase. In other words, dimension has little influence on whether we will beat Laplace mechanism.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_mean_1_1}
\caption{Accuracy measurement based on Hellinger distance wrt. different data variance. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, prior distributions are all $1$ in every dimension}
\label{fig_vs_variance}
\end{figure}

In Fig. \ref{fig_vs_variance}, x-axis are observed data sets of different variances (or means). We study this variable under two-dimension $\betad$ distribution in order to be concise. It shows that our mechanism's accuracy is better when data variance go smaller, meanwhile Laplace mechanism go worse. We will beat Laplace mechanism when observed data are more uniformly.

\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
\label{subsubsec_vs_prior}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{accuracy_vs_prior_5_5_5}
\caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data set is: $[5,5,5]$}
\label{fig_vs_prior}
\end{figure}

In Fig. \ref{fig_vs_prior}, we study this variable under setting that observed data set is $[5,5,5]$ because in Fig. \ref{fig_vs_datasize} Laplace mechanism beat us when data size is 15 and uniformly distributed. The plot shows that in the beginning we cannot beat Laplace but when prior distribution grow larger, we perform better and better and beat Laplace mechanism finally.

\subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
\label{subsubsec_vs_prior_variance}

\begin{figure}[ht]
\centering
\includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\label{fig_vs_prior_variance}
\end{figure}

Here, we change the prior distribution and data variance in the same time. As shown in Fig. \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary. Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.48\textwidth]{global_epsilon_20_20(2).eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure*}

>>>>

\documentclass[sigconf, anonymous]{acmart}

\fancyhf{} % Remove fancy page headers 
% \fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

\setcopyright{none} % No copyright notice required for submissions
% \acmConference[Anonymous Submission to ACM CCS 2017]{ACM Conference on Computer and Communications Security}{Due 19 May 2017}{Dallas, Texas}
% \acmYear{2017}

\settopmatter{printacmref=false, printccs=true, printfolios=true}
\input{macros}

@@

		\item when the prior is $\betad(1,1)$, the observed data set $x = (1,1,0,0,1,1,0,0)$, it is easy to compute the posterior distribution: $\betad(5,5)$, the probability from the two mechanisms are shown in Tab. \ref{tab_8}

		\begin{center}
		\begin{table*}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.83737258593] / 4		$ & 0.0431193490585 & 0.066561234758\\ 
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.662174391701 ] / 3	$ & 0.0785621424847 & 0.0992976939175  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.457635865026 ] / 2	$ & 0.158265808563 & 0.148134752205  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.233629480709 ] / 1	$ & 0.340809715054 & 0.220991081918  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 				$ & 0.37924298484 & 0.329679953964 \\
		 \hline
		\end{tabular}
		\caption{Probability with Prior $\betad(1,1)$ and data size $8$}
		\label{tab_8}
		\end{table*}
		\end{center}

@@

		\item keep the prior unchanged, $\betad(1,1)$, the observed data set $x = (20,20)$ (suppose a black box will produce $A$, $B$ with a certain distribution, after observing this black box continuously for $40$ times, we get $20$ times $A$ and $20$ times $B$, we can get the posterior distribution $\betad(21,21)$ shown in Tab. \ref{tab_40}

		\begin{center}
		\begin{table*}
		 \begin{tabular}{c | c | c} 
		 \hline
		 Hellinger Distance / steps & Our Exponential Mechanism & Laplace Mechanism  \\
		 \hline\hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.999999984481] / \cdots 	$ & 0.000149705644585 & 3.05988187701e-09\\ 
		 \hline
		 \multicolumn{3}{c}{$\cdots$}  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.187421762881] / 2		$ & 0.0548161224677 & 0.0285774941516 \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.110122822057 ] / 1		$ & 0.192227323562 & 0.170131188571  \\
		 \hline
		 $Pr[\hlg(\bysinfer(x), r) = 0.0 ] / 0 					$ & 0.0713016293602 & 0.108688872046 \\
		 \hline
		\end{tabular}
		\caption{Probability with Prior $\betad(1,1)$ and data size $40$}
		\label{tab_40}
		\end{table*}
		\end{center}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{sensitivity}
\label{fig_sensitivity}
\caption{Hellinger distance study}
\end{figure}

@@

\begin{figure}[ht]
\centering
\includegraphics[width=0.48\textwidth]{efficiency}
\label{fig_efficiency}
\caption{Experimental Results for Finding the Local Sensitivity Efficiently}
\end{figure}

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 500$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.45\textwidth]{accuracy_box_2.eps}}
  \subfigure[Data size $n = 300$ with global $\epsilon = 0.5$]{
    \includegraphics[width=0.45\textwidth]{accuracy_box_1.eps}} 
\caption{The experimental results of accuracy of algorithms with Beta prior distribution $\betad(7,4)$ based on Hellinger distance}
\label{fig_beta_hellinger}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[Data size $n = 100$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.08 is Non-Private and with 0.0699407108115 - bound smooth sensitivity 0.09 is (0.8,0.8)-DP]{
    \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_1.eps}}
  \subfigure[Data size $n = 120$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP]{
    \includegraphics[width=0.45\textwidth]{accuracy_dirichlet_hellinger_2.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance}
\label{fig_dirichlet_hellinger}
\end{center}
\end{figure*}

\begin{figure*}
\begin{center}
\centering
  \subfigure[accuracy measurement based on Hellinger distance]{
    \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_hellinger.eps}}
  \subfigure[accuracy measurement based on $l_1$ norm]{
    \includegraphics[width=0.45\textwidth]{accuracy_compare_dirichlet_l1.eps}} 
\caption{The experimental results of accuracy of algorithms with Dirichlet prior distribution $\dirichlet(7, 4, 5)$ based on Hellinger distance and $l_1$  norm, where data size $n = 150$, the exponential mechanism with global sensitivity 0.239992747797 is 0.8 -DP, with local sensitivity 0.0945 is Non-Private, with 0.0677791100173 - bound smooth sensitivity 0.096 is (0.8,0.8)-DP}
\label{fig_dirichlet_hellinger_l1}
\end{center}
\end{figure*}

@@

\begin{figure}[ht]
\begin{center}
\centering
  \subfigure[two dimensions with $\betad (1,1)$ prior distribution]{
    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1.eps}}
  \subfigure[three dimensions with $\dirichlet (1,1,1)$ prior distribution]{
    \includegraphics[width=0.3\textwidth]{accuracy_vs_datasize_1_1_1.eps}} 
\caption{Balanced datasets}
\label{fig_vs_datasize}
\end{center}
\end{figure}

In Figure \ref{fig_vs_datasize} we consider \emph{balanced} datasets of observations.
This means that in the Beta-Binomial setting the datasets will be
half 1s and half 0s, while int the Dirichelet-Multinomial the data will be
equally split in all the $k=3$ bins. Figure \ref{fig_vs_datasize} shows that  when the
data size increases, the accuracy of $\hexpmech$ and $\hexpmechd$
decreases. In Figure \ref{fig_vs_datasize}(a), when the data size is
smaller than 12, $\hexpmech$ can outperform the Laplace mechanism but it fails to do so
for bigger datasets. The same happens in as in Figure \ref{fig_vs_datasize}(b):
the Laplace mechanism starts performing better for datasets bigger than 15.

@@

In Figure  \ref{fig_vs_dimension}, in the x-axis are observed data sets of
different sizes and different dimensions. The plot shows that increasing the number of dimensions have
a similar pejorative effect on $\hexpmech, \hexpmechd$, and the Laplace
mechanism. Fixing the number of dimensions and increasing the data size shows that
the Laplace mechanism is more accurate then both $\hexpmech$ and $\hexpmechd$. 
In other words, dimensions have little influence on whether our mechanisms will beat the Laplace
mechanism.
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_dimension.eps}
\caption{Increasing dimensions and data size with balanced dataset. Priors have 1s in every dimension.}
\label{fig_vs_dimension}
\end{figure}

@@

In Figure \ref{fig_vs_variance}, in the x-axis we considered different levels
of balance of the datasets. We  study this variable only under
two-dimensions $\betad$ distribution in order to be more concise. The plot shows
that $\hexpmech$ accuracy is better than the one of Laplace when the dataset is balanced.

\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_mean_1_1.eps}
\caption{Unbalanced datasets. Prior distributions have 1s in every dimension.}
\label{fig_vs_variance}
\end{figure}

\subsubsection{Accuracy Evaluation wrt. Prior Distribution}
\label{subsubsec_vs_prior}
In Figure \ref{fig_vs_prior}, we fix the dataset to be $\langle 5,5,5\rangle$.
We also considered balanced priors with increasing values in their dimensions.
The plot shows that in the beginning the Laplace mechanism performs better but
it is outperformed after a while.
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{accuracy_vs_prior_5_5_5.eps}
\caption{Observed data set is: $\langle 5,5,5\rangle$, varying balanced priors}
\label{fig_vs_prior}
\end{figure}

% \subsubsection{Accuracy Evaluation wrt. Prior Distribution and Data Variance}
% \label{subsubsec_vs_prior_variance}

% \begin{figure}[ht]
% \centering
% \includegraphics[width=1.0\textwidth]{Accuracy_VS_Prior_mean.eps}
% \caption{Accuracy measurement based on Hellinger distance wrt. different prior distribution and data variances. Settings: $\epsilon = 0.8$ and $\delta = 0.0005$, observed data sets are $[10,10,10]$ and $[1,1,28]$ and prior distributions are range from $[20,20,20]$ to $[76,76,76]$}
% \label{fig_vs_prior_variance}
% \end{figure}

% Here, we change the prior distribution and data variance in the same time. As shown in Fig. \ref{fig_vs_prior_variance}, our exponential mechanism do better in uniform data set than in edging data set while Laplace mechanism on the contrary. Moreover, our mechanism is improving continuously and significantly as prior distribution increasing while Laplace mechanism isn't.

@@

\begin{figure*}
\begin{center}
\centering
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20.eps}}
  \subfigure[data size range from 90 to 180]{
    \includegraphics[width=0.45\textwidth]{global_epsilon_20_20(2).eps}} 
\caption{Concrete privacy calculation under settings that: prior distribution:$[1,1]$, $\epsilon = 0.8$, $\delta = 0.0005$ and observed data are uniformly distributed}
\label{fig_privacy}
\end{center}
\end{figure*}
